---
title: "Second Proyect"
author: "Cristian Riveros"
date: "6/18/2019"
output:
  html_document: default
  pdf_document: default
---


# Learning ggplot2

We're learning ggplot2 It's going to be amazing. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Including Plots

You can also embed plots, for example:


```{r cars}


ohi_data <- read.csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/OHI_global_data.csv")

head(ohi_data)

summary(ohi_data)

table(ohi_data$georegion_two)

library(ggplot2)
#ggplot(data = ohi_data, aes(x = georegion_one, y =OHI_score)) + 
#geom_point()


ggplot(data = ohi_data, aes(x = OHI_score, y = HDI, size = coastal_pop)) + 
  geom_jitter(width=0.2)

```

Boxplot

`````{r bloxplot}

ggplot(data = ohi_data, aes(x = georegion_one)) + 
  geom_bar()
```
Histogram
```{r Histogram}

ggplot(data = ohi_data, aes(x = HDI)) + 
geom_histogram() 

```



## Including Plots

You can also embed plots, for example:

```{r multiples geoms}

ggplot(data = ohi_data, aes(y=OHI_score, x = HDI, color=georegion_one)) +
  geom_point()

```


```{r multiples geoms}


ggplot(data = ohi_data) +
geom_point(aes(y = OHI_score, x = HDI, color=georegion_one))  



```


Adding a 

``` {r}

ggplot(data=ohi_data, aes(x= OHI_score, y = HDI,
color = coastal_pop))+
  geom_point()


```

adding a third discrete variable

``` {r}




ggplot(data=ohi_data, aes(x= OHI_score, y = HDI,
                            color=georegion_one))+
geom_point()

ggplot(data=ohi_data, aes(x= OHI_score, y = HDI,
shape=georegion_one))+

geom_point()


  
```

  Adding others
  
```{r}

ggplot(data = ohi_data, aes(y = OHI_score, x = HDI, color=georegion_one)) + 
  geom_point() + 
    labs(y = "OHI score, 2017",
       x = "Human Development Index",
       title = "Countries with high human development have more sustainable oceans",
      color = "Georegion") +  # if color doesn't work, use "fill"
     theme_bw()
```
  
  other forms to describes that
  
```{r}

library(ggplot2)
  
  ggplot(data = ohi_data, aes(x = OHI_score, y = OHI_trend, color = HDI)) + 
  geom_point(size =2) +
  scale_colour_gradientn(colors = c("blue", "red"))
  
```  
  
Other

``` {r}
  my_palette <- brewer.pal(n=12, "Set3")

ggplot(data = ohi_data, aes(x = OHI_score, y = HDI, color = georegion_one)) + 
  geom_point(size = 3) +
  scale_color_manual(values = my_palette)
  
```
  
  

  
  


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
