---
title: "Tidy_session"
author: "Cristian Riveros"
date: "6/19/2019"
output: html_document
---
 
 load tidyverse
```{r}

library (tidyverse)

```

Load data

```{r}

gapminder <- readr::read_csv('https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/gapminder.csv') 


```

```{r}
head(gapminder)
tail (gapminder)


str(gapminder)

names(gapminder)

ncol(gapminder)

summary(gapminder)

#library(skimr) # install.packages('skimr')
#skim(gapminder)

```

Look at individual dataframe

```{r}
gapminder$lifeExp
gapminder$continent



```

Learning the `filter()` function

```{r}

filter(gapminder, lifeExp < 29)

#
filter(gapminder, country == "Mexico")

```
exercise using filter

What was the average life expectency in Brazil between 1987 and 2007?
Hint: do this in 2 steps by assigning a variable and then using the mean() function.



```{r}
x <- filter(gapminder, country == "Brazil", year > 1986)
mean(x$lifeExp)
min(x$lifeExp)



```

learning operator 'select()`

```{r}
select(gapminder, year, country, lifeExp)
select(gapminder, -continent, -gdpPercap, -pop)

```

Using `filter` and `select` 

```{r}
gap_cambodia <- filter(gapminder, country=="Cambodia")
gap_cambodia2 <- select(gap_cambodia, -continent, -lifeExp)

```

Learning pipe function

```{r}
gapminder %>% head()
head(gapminder)


## instead of this...
gap_cambodia  <- filter(gapminder, country == "Cambodia")
 select(gap_cambodia, -continent, -lifeExp) 

## ...we can do this
gap_cambodia  <- gapminder %>% 
  filter(country == "Cambodia") %>% 
  select(-continent, -lifeExp) 

```


Lear `mutate``

```{r}


mutate (gapminder,gdp = pop *gdpPercap)

gapminder %>% 
  mutate (gdp= pop *gdpPercap)


```

Calculate the population in thousands for all Asian countries in the year 2007 and add it as a new column.

```{r}

gap_Asia_continent <- filter(gapminder, continent=="Asia", year == 2007) %>% 
  mutate(New_columm= pop/1000 )

```

Learning the `group_by()`

```{r}

gapminder %>% 
  filter(year==2002) %>% 
  group_by(continent) %>% 
  mutate( cont_pop = sum(pop))
  
```

add in `summarize`

```{r}
gapminder %>% 
  filter(year==2002) %>% 
  group_by(continent) %>% 
  summarize(cont_pop =sum(pop))
  
  

```


```{r}
gapminder %>% 
  filter(year==2002) %>% 
  group_by(continent,year) %>% 
  summarize(cont_pop =sum(pop))
  
```